Races with hyper3 objects

### 2022-06-26 inst/race3.Rmd
another figure

@@

>>>>

## Three competitors

@@

### all results for AAB

* $A\succ A\succ B\longrightarrow\frac{a^2}{1+a}$
* $A\succ B\succ A\longrightarrow\frac{1-2a-a^2}{(1+a)^2}$
* $B\succ A\succ A\longrightarrow\frac{1-a}{1+a}$

Graphically

```{r}
f_aab <- function(a){a^2/(1+a)}
f_aba <- function(a){a*(1-a)/(1+a)^2}
f_baa <- function(a){(1-a)/(1+a)}

p <- function(f,...){points(a,f(a)/max(f(a)),...)}
plot(0:1,0:1,xlab="p(a)",ylab="Likelihood",type="n")
p(f_aab,type="l",col="black")
p(f_aba,type="l",col="red")
p(f_baa,type="l",col="blue")
legend(x=0.85,y=0.7,col=c("black","red","blue"),lty=1,pch=NA,legend=c("AAB","ABA","BAA"))
abline(h=exp(-2),lty=2)
```

## Four competitors
